### 2014-06-03 ACL2014/system.tex
Updated experiments, discussion

\section{Approach}
\label{sec:approach}
We describe a distributed \lshf framework based on map-reduce. 
First, we present vanilla \lsh algorithm based on the seminal work of Andoni and Indyk  \shortcite{Andoni08CACM}. 
To best of our knowledge, this is the first paper that applies this variant of locality sensitive hashing algorithms to NLP applications.

The algorithm in \cite{Andoni08CACM} improves the existing research in \lsh and \plebf (PLEB) \cite{Indyk98STOC,Charikar02STOC}. 
PLEB was applied for noun clustering \cite{ravichandran05} and speech tasks \cite {JansenASRU11,JansenIS12}. 
Recent prior work on new variants of PLEB \cite{goyal12Flag} for distributional similarity can be seen as 
implementing a special case of Andoni and Indyk's \lsh algorithm.

@@

In order to increase the recall of the \lsh algorithm, the algorithm of Andoni et al. then uses
$L$ hash tables, each constructed using a different $g_j(\cdot)$ function, where each 
$g_j(\cdot)$ is defined as $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q)))$; $\forall 1 \leq j \leq  L$.

@@

@@

%To solve the above problem, we propose a distributed Hadoop framework based on Locality Sensitive Hashing. 
%Our framework has three main steps
%i) Generate $256$ bit signature for each query.  
%ii) Use the $256$ bit signature for each query to generate $L$ tables for each table with $K$ bit signature. 
%Next, generate query pairs which fall in the same table.
%iii) Compute cosine similarity between query terms which fall in the same table and return the query pairs  
%with similarity $\geq\tau$.  
%
Figure~\ref{alg:lsh} describes the algorithm for both creating the data structure, as well as for
querying it. In preprocessing step, the algorithm takes as input $N$ queries along with the associated feature vectors. 
In our setting, each query is represented using an extremely sparse and high dimensional feature vector
that is constructed as follows: for query $q$, we take all the webpages (urls) that any user has clicked on 
when querying for $q$. Using this representation, we then generate the 
$L$ different hash values for each query $q$, where each such hash value is again 
the concatenation of $K$ hash functions. These $L$ hash values per query are then used to create $L$ hash tables.
Since the width of the index of each bucket is $K$, each hash table contains at most $2^K$ buckets. 
Each query term is then placed in their respective buckets for each of the $L$ hash tables.

@@

\begin{figure}
\fbox{
\begin{minipage}{2.5in}
{\bf Preprocessing:} Input is $N$ queries with their respective feature vectors.
\begin{itemize}
\item Select $L$ functions $g_j$, $j=1,2,\dots,L$, setting  $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q))$, where 
$\{h_{i,j}, i\in [1, K], j\in [1,L]\}$ are chosen at random from the \lsh family.
\item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. 
All queries with the same $g_j$ value ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
\end{itemize}

\subsection{Reusing Hash Functions}
\label{subsec:resuseHash}
In Section \ref{subsec:vlsh:cosine}, we showed that vanilla \lsh requires $L\times K$ hash functions. 
However generating hash functions is computationally expensive as 
it takes time to read all features and 
evaluate hash functions over all those features to generate a single bit. 
To minimize the number of hash functions computations, 
we use a trick from Andoni and Indyk \shortcite{Andoni08CACM} 
in which hash functions are reused to generate $L$ tables. $K$ is assumed to be even and $R \approx	\sqrt L$. 
We generate $f(q)=(h_1(q),h_2(q),\dots,h_{K/2}(q)))$ of length $k/2$. 
Next, we define $g(q)=(f_a,f_b)$, where $1\leq a < b \leq R$. Using such pairing, we
can thus generate $L= \frac{R (R -1)}{2}$ hash indices. 
This scheme requires O($K  \sqrt L$) hash functions, instead of O($KL$).    
For rest of this paper, we use the above trick to generate $L$ hash tables with bucket indices of width $K$ bits.  
\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{ll}
\hline
\hline
 \textbf{Symbol} &  \textbf{Description} \\
\hline 
$N$ & \# of query terms \\
$D$ & \# of features i.e. all clicked unique urls \\
\hline
\multirow{3}{*}{$K$} & \# of hash functions concatenated together \\ 
   & $g(q)=(h_1(q),h_2(q),\dots,h_k(q)))$ \\ 
	 & to generate the index of a table \\
\hline
 \multirow{2}{*}{$L$} & \# of tables generated independently \\ 
	  &  with $g_j(q)$ index, $\forall 1 \leq j \leq  L$  \\
\hline
$F$ & \# of bits flipped, $\forall 1 \leq j \leq  L$   \\
$\tau$ & $\tau$ threshold \\
Recall & fraction of similar candidates retrieved \\
Comparisons & Avg \# of pairwise comparisons per query  \\
\hline 
\end{tabular}
\caption{\footnotesize{Major Notations}}
}
\label{tab:notation}
\end{table}

>>>>

\section{Proposed Approach}
\label{sec:approach}
We describe a distributed \lshf framework based on map-reduce. 
First, we present vanilla \lsh algorithm based on the seminal work of Andoni and Indyk  \shortcite{Andoni08CACM}. 
To best of our knowledge, this is the first paper that applies this variant of locality sensitive hashing algorithms to NLP applications.

The algorithm in Andoni and Indyk \shortcite{Andoni08CACM} improves the existing research in \lsh and \plebf (PLEB) \cite{Indyk98STOC,Charikar02STOC}. 
PLEB was applied for noun clustering \cite{ravichandran05} and speech tasks \cite {JansenASRU11,JansenIS12}. 
Recent prior work on new variants of PLEB \cite{goyal12Flag} for distributional similarity can be seen as 
implementing a special case of Andoni and Indyk's \lsh algorithm.

@@

In order to increase the recall of the \lsh algorithm, the algorithm of Andoni et al. then uses
$L$ hash tables, each constructed using a different $g_j(\cdot)$ function, where each 
$g_j(\cdot)$ is defined as $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q)))$; $\forall 1 \leq j \leq  L$. 
We list the major notations of \lsh in Table \ref{tab:notation}.

\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{ll}
\hline
\hline
 \textbf{Symbol} &  \textbf{Description} \\
\hline 
$N$ & \# of query terms \\
$D$ & \# of features i.e. all clicked unique urls \\
\hline
\multirow{3}{*}{$K$} & \# of hash functions concatenated together \\ 
   & $g(q)=(h_1(q),h_2(q),\dots,h_k(q)))$ \\ 
	 & to generate the index of a table \\
\hline
 \multirow{2}{*}{$L$} & \# of tables generated independently \\ 
	  &  with $g_j(q)$ index, $\forall 1 \leq j \leq  L$  \\
\hline
$F$ & \# of bits flipped, $\forall 1 \leq j \leq  L$   \\
$\tau$ & $\tau$ threshold \\
Recall & fraction of similar candidates retrieved \\
Comparisons & Avg \# of pairwise comparisons per query  \\
\hline 
\end{tabular}
\caption{\footnotesize{Major Notations}}
\label{tab:notation}
}
\end{table}

@@

\begin{figure}[ht]
\small
\fbox{
\begin{minipage}{2.5in}
{\bf Preprocessing:} Input is $N$ queries with their respective feature vectors.
\begin{itemize}
\item Select $L$ functions $g_j$, $j=1,2,\dots,L$, setting  $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q))$, where 
$\{h_{i,j}, i\in [1, K], j\in [1,L]\}$ are chosen at random from the \lsh family.
\item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. 
All queries with the same $g_j$ value ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
\end{itemize}

@@

%To solve the above problem, we propose a distributed Hadoop framework based on Locality Sensitive Hashing. 
%Our framework has three main steps
%i) Generate $256$ bit signature for each query.  
%ii) Use the $256$ bit signature for each query to generate $L$ tables for each table with $K$ bit signature. 
%Next, generate query pairs which fall in the same table.
%iii) Compute cosine similarity between query terms which fall in the same table and return the query pairs  
%with similarity $\geq\tau$.  
%
Figure~\ref{alg:lsh} describes the algorithm for both creating the data structure, as well as for
querying it. In preprocessing step, the algorithm takes as input $N$ queries along with the associated feature vectors. 
In our setting, each query is represented using an extremely sparse and high dimensional feature vector
that is constructed as follows: for query $q$, we take all the webpages (urls) that any user has clicked on 
when querying for $q$. Using this representation, we then generate the 
$L$ different hash values for each query $q$, where each such hash value is again 
the concatenation of $K$ hash functions. These $L$ hash values per query are then used to create $L$ hash tables.
Since the width of the index of each bucket is $K$ with each coordinate being $0/1$ bit, each hash table contains at most $2^K$ buckets. 
Each query term is then placed in their respective buckets for each of the $L$ hash tables.

@@

\subsection{Reusing Hash Functions}
\label{subsec:resuseHash}
In Section \ref{subsec:vlsh:cosine}, we showed that vanilla \lsh requires $L\times K$ hash functions. 
However generating hash functions is computationally expensive as 
it takes time to read all features and 
evaluate hash functions over all those features to generate a single bit. 
To minimize the number of hash functions computations, 
we use a trick from Andoni and Indyk \shortcite{Andoni08CACM} 
in which hash functions are reused to generate $L$ tables. $K$ is assumed to be even and $R \approx	\sqrt L$. 
We generate $f(q)=(h_1(q),h_2(q),\dots,h_{K/2}(q)))$ of length $k/2$. 
Next, we define $g(q)=(f_a,f_b)$, where $1\leq a < b \leq R$. Using such pairing, we
can thus generate $L= \frac{R (R -1)}{2}$ hash indices. 
This scheme requires O($K  \sqrt L$) hash functions, instead of O($KL$).    
For rest of this paper, we use the above trick to generate $L$ hash tables with bucket indices of width $K$ bits.
